Realizability-Preserving Two-Moment DG Method for Fermionic Transport \tnoteref{ldrd-support}

### 2018-01-31 Documents/M1/realizableFermionicM1/sections/realizability.tex
Added the plots of Mab.

\begin{lemma}
  Let $\big\{\cJ_{a},\vect{\cH}_{a},\vect{\cK}_{a}\big\}$ be defined as in Eq.~\eqref{eq:angularMoments} with distribution function $f_{a}\in[0,1]$.  
  Similarly, $\big\{\cJ_{b},\vect{\cH}_{b},\vect{\cK}_{b}\big\}$ be moments of a distribution function $f_{b}\in[0,1]$.  
  Let $\Phi^{\pm}(\vect{\cM})=\f{1}{2}\big(\vect{\cM}\pm\widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cM})\big)$, where $\widehat{\vect{e}}\in\bbR^{3}$ is an arbitrary unit vector and $\vect{\cF}(\vect{\cM})=\big(\vect{\cH},\vect{\cK}\big)^{T}$.  
  Then
  \begin{equation}
    \vect{\cM}_{ab} \equiv \Phi^{+}(\vect{\cM}_{a})+\Phi^{-}(\vect{\cM}_{b})\in\cR.
  \end{equation}
\end{lemma}
\begin{proof}
  Using the same treatment we made in proof of Lemma~\ref{lem: MomentRealizable}, we can rewrite the first component of $\vect{\cM}_{ab}$ as
  \begin{align*}
  \f{1}{2}\big(\vect{\cJ_{a}} + \widehat{\vect{e}}\cdot\vect{\cH_{a}}+\vect{\cJ_{b}} - \widehat{\vect{e}}\cdot\vect{\cH_{b}}\big) = &\f{1}{2} \left\lbrace \f{1}{2}\int_{\bbS^{1}}\left[ \mathfrak{f}_{a}(\mu)\,(1+\mu) + \mathfrak{f}_{b}(\mu)\,(1-\mu)\right] \,d\mu \right\rbrace \\
  \equiv  &\f{1}{2}\int_{\bbS^{1}} \mathfrak{f}_{ab}(\mu)\,d\mu
  \end{align*}
  where $\mathfrak{f}_{ab}(\mu) \equiv \f{1}{2}\left[ \mathfrak{f}_{a}(\mu)\,(1+\mu) + \mathfrak{f}_{b}(\mu)\,(1-\mu)\right]$ and $\mathfrak{f}_{ab}(\mu)\in[0,1]$.
  And the second component is
  \begin{align*} 
   \f{1}{2}\big(\vect{\cH_{a}} + \widehat{\vect{e}}\cdot\vect{\cK_{a}}+\vect{\cH_{b}} - \widehat{\vect{e}}\cdot\vect{\cK_{b}}\big) =
   &\f{1}{2} \left\lbrace \f{1}{2}\int_{\bbS^{1}}\left[ \mathfrak{f}_{a}(\mu)\,(1+\mu) + \mathfrak{f}_{b}(\mu)\,(1-\mu)\right]\mu \,d\mu \right\rbrace \\
   \equiv  &\f{1}{2}\int_{\bbS^{1}} \mathfrak{f}_{ab}(\mu)\,\mu d\mu. 
  \end{align*}
  Applying Lemma~\ref{lem: MomentRealizable}, we know that $\vect{\cM}_{ab}\in\cR$.
\end{proof}

@@

>>>>

\begin{lemma}
  Let $\big\{\cJ_{a},\vect{\cH}_{a},\vect{\cK}_{a}\big\}$ be defined as in Eq.~\eqref{eq:angularMoments} with distribution function $f_{a}\in[0,1]$.  
  Similarly, $\big\{\cJ_{b},\vect{\cH}_{b},\vect{\cK}_{b}\big\}$ be moments of a distribution function $f_{b}\in[0,1]$.  
  Let $\Phi^{\pm}(\vect{\cM})=\f{1}{2}\big(\vect{\cM}\pm\widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cM})\big)$, where $\widehat{\vect{e}}\in\bbR^{3}$ is an arbitrary unit vector and $\vect{\cF}(\vect{\cM})=\big(\vect{\cH},\vect{\cK}\big)^{T}$.  
  Then
  \begin{equation}
    \vect{\cM}_{ab} \equiv \Phi^{+}(\vect{\cM}_{a})+\Phi^{-}(\vect{\cM}_{b})\in\cR.
  \end{equation}
\end{lemma}
\begin{proof}
  Using the same treatment we made in proof of Lemma~\ref{lem: MomentRealizable}, we can rewrite the first component of $\vect{\cM}_{ab}$ as
  \begin{align*}
  \f{1}{2}\big(\vect{\cJ_{a}} + \widehat{\vect{e}}\cdot\vect{\cH_{a}}+\vect{\cJ_{b}} - \widehat{\vect{e}}\cdot\vect{\cH_{b}}\big) = &\f{1}{2} \left\lbrace \f{1}{2}\int_{\bbS^{1}}\left[ \mathfrak{f}_{a}(\mu)\,(1+\mu) + \mathfrak{f}_{b}(\mu)\,(1-\mu)\right] \,d\mu \right\rbrace \\
  \equiv  &\f{1}{2}\int_{\bbS^{1}} \mathfrak{f}_{ab}(\mu)\,d\mu
  \end{align*}
  where $\mathfrak{f}_{ab}(\mu) \equiv \f{1}{2}\left[ \mathfrak{f}_{a}(\mu)\,(1+\mu) + \mathfrak{f}_{b}(\mu)\,(1-\mu)\right]$ and $\mathfrak{f}_{ab}(\mu)\in[0,1]$.
  And the second component is
  \begin{align*} 
   \f{1}{2}\big(\vect{\cH_{a}} + \widehat{\vect{e}}\cdot\vect{\cK_{a}}+\vect{\cH_{b}} - \widehat{\vect{e}}\cdot\vect{\cK_{b}}\big) =
   &\f{1}{2} \left\lbrace \f{1}{2}\int_{\bbS^{1}}\left[ \mathfrak{f}_{a}(\mu)\,(1+\mu) + \mathfrak{f}_{b}(\mu)\,(1-\mu)\right]\mu \,d\mu \right\rbrace \\
   \equiv  &\f{1}{2}\int_{\bbS^{1}} \mathfrak{f}_{ab}(\mu)\,\mu d\mu. 
  \end{align*}
  Using Lemma~\ref{lem: MomentRealizable}, we know that $\vect{\cM}_{ab}\in\cR$ and can be written as $\vect{\cM}_{ab}(\cJ_{ab},\vect{\cH}_{ab})$.
\end{proof}

@@

\begin{figure}[h!]
  \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width=\textwidth]{figures/MabWithMI}
    \caption{$\vect{\cM}_{ab}$ with Minerbo closure.}
  \end{subfigure}
  %
  \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width=\textwidth]{figures/MabWithBLKS}
    \caption{$\vect{\cM}_{ab}$ with Kershaw closure.}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width=\textwidth]{figures/MabWithCBME}
    \caption{$\vect{\cM}_{ab}$ with Chernohorsky \& Bludman maximum entropy closure.}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width=\textwidth]{figures/MabWithBLME}
    \caption{$\vect{\cM}_{ab}$ with Banach \& Larecki maximum entropy closure.}
  \end{subfigure}
  \label{fig:MabWithDifferentClosure}
\end{figure}
